Hydra Battles and Cie

### 2021-02-25 doc/part-hydras.tex
removed useless notation scopes

Lemma LF2 : forall i, (exp2 i * i < F_ 2 i)%nat.
\end{Coqsrc}

@@

Theorem F_alpha_ge_S alpha : forall n, (n < F_ alpha n)%nat.

@@

Theorem F_alpha_beta alpha : forall beta n, Canon_plus n alpha beta -> 
                                        (F_ beta n <= F_ alpha n)%nat.
\end{Coqsrc}

>>>>

Lemma LF2 : forall i, exp2 i * i < F_ 2 i.
\end{Coqsrc}

@@

Theorem F_alpha_ge_S alpha : forall n, n < F_ alpha n.

@@

Theorem F_alpha_beta alpha : 
forall beta n, Canon_plus n alpha beta -> 
                                        F_ beta n <= F_ alpha n.
\end{Coqsrc}
